\chapter{Introduction}
\pagenumbering{arabic} 
\setcounter{page}{1}

\section{Motivation}
\label{sec:motivation_intro}
A web application aiming to forecast football match results is nothing new. However, most of the existing solutions either overwhelm their users with unstructured statistics or work as a self-contained black-box prediction tool preventing the users from participating in the process of prediction. The proposed system will provide its users with all necessary information to support their betting decision and allow them to take full control over the prediction output. To the best of my knowledge no other software offers the same experience as the one proposed in this dissertation.

\section{Target Audience}
\label{sec:targetaudience_intro}
The intended users of the application will be people with interest in football, more specifically in betting. With this in mind, the age range of potential users will be 18 and up.

\section{Problems Addressed}
\label{sec:problemsaddressed_intro}

\subsection*{Problem 1 - Football punters would like to see all the statistics required for making a prediction in one place.}
When betting on football, there is always a temptation to base a betting decision on a opinion of someone else or use a prediction software. However, experts can be wrong or not even following their own forecasts. It can also be quite confusing, which particular expert’s prediction to follow, and after all, opinions of different experts will probably contradict. 

On the opposite side, a professional football punter will spend a lot of time gathering and analysing statistics about a football match (possibly, just using a notepad and a pen). The application proposed in this dissertation will do this job for the user. It will aggregate all the data that may affect the outcome of an upcoming match and also compare it for the participating teams.

Among other benefits, the easy access to relevant data will hopefully encourage application users to make betting decisions based on facts rather that an impulse or other punters’ advice.

\subsection*{Problem 2 - Punters would like to be able to make own predictions.}
The choice of factors that can influence a football match result will differ depending on a punter's betting system. The users of the proposed application will be able to create their own betting system by picking their factors and assigning them a weighing percentage, having the power to influence the prediction output.

\subsection*{Problem 3 - Football punters rarely monitor their betting results.}
Learning from the past mistakes is a key to becoming successful in any activity. The application will offer a way to monitor the performance of user's betting system in order to be able to improve it over time. 

\section{Project Aims \& Objectives}
\label{sec:objectives_intro}
The overall aim of this project is to build a betting game simulator that provides an effective solution to the above problems and enables its users creating an effective betting system in the long run. 

\section{Report Structure}
\label{sec:reportstructure_intro}
This report will describe the research, design and implementation of the application, as well as justification of the decisions made throughout the project.
The structure of the report is outlined below. 

\begin{itemize}
	\item Chapter 1 \emph{Introduction}
	\item Chapter 2 \emph{Background studies and Objectives}, introduces the reader to the history of online gambling, outlines the project objectives, addresses the legal, social and ethical issues.
	\item Chapter 3 \emph{Requirements Analysis}, describes the processes occuring during the process of requirement analysis, such as target audience reasearch and analysing the existing solutions. The chapter also contains the final list of project mandatory and optional requirements.
	\item Chapter 4 \emph{Application Prototype}, describes the process of designing the application.
	\item Chapter 5 \emph{Implementation}, describes the process of building the application.
	\item Chapter 6 \emph{Testing \& Evaluation}, evaluates the overall project and provides results of tests carried out.
	\item Chapter 7 \emph{Conclusion}
\end{itemize} 
