\chapter{Legal, Social and Ethical Issues}
\label{ch:LESP_issues}
In this chapter the legal, social and ethical issues relating to the application are addressed.  

\section{Legal Issues}
\label{sec:legalissues_lesp}
There are a number of legal considerations to take into account when working on an application and also once it is a finished product to be used by the public.

The application will store some basic user data in its database. Therefore, the application must take all the necessary precautions to protect the stored data and sensitive information. The application will not disclose the personal data of its users to any third parties.

The final product must adhere to all the relevant UK legislation, this would include the Data Protection Act of 1998, which has in it many relevant laws pertaining to online products.  In particular if the website was ever to make a profit either by advertising or sales or any other way, it would need to be registered with the appropriate government department. As it stands, it does not because it makes no money, but that would have to be looked into if the application was going to be developed along those lines. Also the usual anti discriminatory laws would have to be followed, meaning it cannot be biased against users because of their sex, nationality, colour or disabilities.

Less a legal and more a professional consideration is that the application should not try to mislead a user in any way, anything it can do should not be exaggerated, in this particular application there is nothing on the site saying that the predictions are going to be 100% accurate every time. Also, it is important that even though each prediction module can be weighted in importance by the user, the computational logic of each module has to be sound.

\section{Social Issues}
\label{sec:socialissues_lesp}
There are several advantages of using the application for serious and not so serious gamblers alike. The main goal of using the application is to maximise the amount of correctly predicted results. Using and refining the prediction system should lead to more informed bets and hopefully remove any rash or less thought out bets that sometimes plague a gambler. Secondly, the use of  the application will save what can be a large amount of  time spent on gathering information before making a betting decision.

On the other hand,  the application will hold some interest even for non gambling football fans. Every football fan has an opinion on who is going to win a match and more importantly why they are going to win, this application gives them a chance to prove it. By including a league table showing how the users rate against each other and in the future having more community focussed features mean that the application will offer something other than just a gambling tool.

\section{Ethical Issues}
\label{sec:ethicalissues_lesp}
There are a few ethical matters to consider when coming up with any new application, or indeed any new venture at all. For example, using illegal or pirated software, abusing open source code without proper accreditation or reverse engineering a piece of code to find out how it works then using that to improve your own software.  

On this project there was no illegal software used and no reverse engineering done. Open source code that had a GPL (General Public License) was used. A GPL describes how an author would like the code to be distributed, copied or modified and was followed on this project correctly as well as all credit given where due.  

There are ethical issues outside of the area of software development to consider as well, namely the ones relating to gambling in general. Gambling is not illegal but nevertheless it does have it’s share of controversy and is frowned upon in many circles. Gambling addiction is also a very big problem for a lot of people and feeding that addiction would be ethically wrong. However, this application does not require you to bet at all and does not link to any gambling websites. In general, the application is not aimed at promoting gambling. A user can get plenty of enjoyment and use out of it without ever risking any money.  Moreover, it supports a more sensible and measured approach to football betting and by tracking a user’s performance can show whether or not a person should be gambling in the first place.