\chapter{Professional Considerations}
\label{ch:ProfConsiderations}
In this chapter the background of the project will be discussed. The chapter will take the reader through the history of sports betting with a particular focus on online gambling. The primary and the extended objectives of the project will be outlined and the professional considerations will be addressed. 

\section{History And General Information}
\label{sec:history_back}
!!!For this chapter put lots of references (especially in the BG subchapter)

Gambling is nothing new. Since time began, people have been betting on the outcome of an event, be that the victor in a gladiator competition, the winning team in a football match, or the first horse past the finishing post.


People have always been interested in games with the element of luck and therefore gambling is one of the oldest forms of entertainment of mankind. The rise of the Internet and mobile devices has made remote gambling more available for a wide variety of users. The reason for that could be that Internet applications and websites can be are easily accessed 24/7. Amongst the most popular types of online gambling can be found card games, dice games, electronic games (such as poker), betting on sporting events, etc.
Sports betting is no longer associated solely with horse racing. Among all types of sports gambling, football gambling is a leading industry with a share about 70% and half a million people betting weekly all over the world.
When it comes to any sports betting (football betting including), the user is trying to predict the result of the event and placing the money on the outcome. This prediction can be made based on a “hunch” or by using logic and domain knowledge, in a lot of cases by both combined. Naturally, this gave rise to a vari- ety of betting software systems that are attempting to predict the next match re- sult. Most of the time those betting systems work as a “black box” not allowing the user to influence the prediction output and preventing the user from understand- ing the exact logic used inside the system.
Football bettor can have various strategies when making a betting decision. As mentioned above, the user can buy a prediction software and simply follow the tips suggested by that system. Another option is to make a decision influenced by the opinion of the other tipsters, experts’ opinions or rumours. However, if the aim is to achieve sustainable profit (or minimise the loss from betting) , most experi- enced bettors would ignore betting tips and predictions of others and go for the pure facts trying to make their own prediction. To make this happen, the bettor has to aggregate several pieces of information from various sources. This action has to be repeated for every single match.
From my experience, the necessity to repeat an action many times could lead to a creation of interesting software solutions. That is how I got inspired to create an application that would aggregate this information for the user and therefore act as an interactive decision supporting system.


\section{Social, legal and ethical issues}
\label{sociallegalethicalissues_back}

\subsection{Legal Issues}
\label{leaglissues_back}
???
Finding affordable data source for the future application may become a non-trivial task. Therefore, I am considering using “web scraping” as one of the options to load most recent football data into the system. It can be said that there is a fine line between collecting information using the “web scraping” technique and stealing it. Most of the websites have a copyright disclosure defining the rules for the use of the information they provide. Thus, I will carefully read the disclosure statements and follow them along legally and ethically. 

\subsection{Ethical Issues}
\label{ethicalissues_back}
Due to the nature of the application it is inevitable that it will store some basic user data in its database. The application must take all the necessary precautions to protect the stored data and sensitive information. The application will not disclose personal data of its users to any third parties.

\subsection{Social Issues}
\label{socialissues_back}
There are several advantages of using the application for a rational punter. First,  the use of application will save time spent on gathering information before making a betting decision. Secondly, the use of it will lead its users to more thoughtful and measured approach to football betting. 

\subsection{Professional Considerations}
\label{prof_back}
Although the main aim of the application is to provide transparent prediction to the user, there is still certain amount of calculation happening in the background. I assume that user will trust the betting system when making a betting decision. Therefore ensuring the accuracy of the calculations and providing good test coverage is a very important part of the application development.